Analysis of Odd one out experiment

### 2019-06-06 reports/odd_one_out/analysis_oddoneout.Rmd
one sample ttest and some figure polishing

```{r}
p <- df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  theme(text = element_text(size=18)) +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4"))
p
ggsave(file.path(plots_dir, "opam_figure.eps"), p, width = 6, height = 6)

df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  facet_wrap(~subject_id) +
  geom_hline(yintercept = 1/9) 
```

@@

```{r lmer - quintiles}
library(lme4)

glm1 <- glmer(correct ~ quintile + (1+quintile|subject_id) + (1+quintile|category), df, family = binomial())
glm1_null <- glmer(correct ~ (1+quintile|subject_id) + (1+quintile|category), df, family = binomial())
anova(glm1, glm1_null)

@@

# Express the distances as ratio

>>>>

```{r}
p <- df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  theme(text = element_text(size=18)) +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) + 
  ylab("Správnost odpovědí") + xlab("Kvintil")
p
ggsave(file.path(plots_dir, "Fig_chp3_.eps"), p, width = 6, height = 6)

df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  theme(text = element_text(size=18)) +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) + 
  ylab("Správnost odpovědí") + xlab("Kvintil") +
  facet_wrap(~subject_id)

@@

```{r lmer - quintiles}
glm1 <- glmer(correct ~ quintile + (1|subject_id) + (1|category), df, family = binomial())
glm1_null <- glmer(correct ~ (1|subject_id) + (1|category), df, family = binomial())
anova(glm1, glm1_null)

@@

```{r}
df_for_onettest <- df %>% group_by(subject_id,quintile) %>% summarize(correct = mean(correct))
df_for_onettest %>% group_by(quintile) %>% do(t.test(.$correct, mu = 1/9) %>% broom::tidy())
df_for_onettest %>% group_by(quintile) %>% do(d=lsr::cohensD(.$correct, mu = 1/9)) %>% mutate(d = unlist(d))

```
# Express the distances as ratio
